
        @misc{readelfheapbufferoverflow,
          title = {Readelf heap buffer overflow(CVE-2019-9077).},
          url = {https://nvd.nist.gov/vuln/detail/CVE-2019-9077},
        }
        
        @misc{luaheapbufferoverflow,
          title = {Lua heap buffer overflow(bug #5.0-2).},
          url = {https://www.lua.org/bugs.html#5.0-2},
        }
        
        @misc{libzipuseafterfree,
          title = {Libzip use after free(CVE-2017-9746).},
          url = {https://nvd.nist.gov/vuln/detail/CVE-2017-9746},
        }
        
        @misc{nmstackbufferoverflow,
          title = {Nm stack buffer overflow(Bugzilla-21670).},
          url = {https://sourceware.org/bugzilla/show_bug.cgi?id=21670},
        }
        
        @misc{tcpdumpheapbufferoverflow,
          title = {Tcpdump heap buffer overflow(CVE-2017-16808).},
          url = {https://nvd.nist.gov/vuln/detail/CVE-2017-16808},
        }
        
        @misc{sleuthkitdoublefree,
          title = {Sleuthkit double free(issue-905).},
          url = {https://github.com/sleuthkit/sleuthkit/issues/905},
        }
        
        @misc{patchheapbufferoverflow,
          title = {Patch heap buffer overflow(bug #54558).},
          url = {https://savannah.gnu.org/bugs/?func=detailitem&item_id=54558},
        }
        
        @misc{perlheapbufferoverflow,
          title = {Perl heap buffer overflow(issue-17384).},
          url = {https://github.com/Perl/perl5/issues/17384},
        }
        
        @misc{mrubyuninitializedvariable,
          title = {Mruby uninitialized variable(issue-3947).},
          url = {https://github.com/mruby/mruby/issues/3947},
        }
        
        @misc{mrubytypeconfusion,
          title = {Mruby type confusion(hackerone-185041).},
          url = {https://hackerone.com/reports/185041},
        }
        
        @misc{mrubyheapbufferoverflow,
          title = {Mruby heap buffer overflow(CVE-2018-12248).},
          url = {https://sourceware.org/bugzilla/show_bug.cgi?id=24243},
        }
        
        @misc{pythonheapbufferoverflow,
          title = {Python heap buffer overflow(oss-sec-2020/ql/65).},
          url = {https://bugs.python.org/issue26171},
        }
        
        @misc{mrubyintegeroverflow,
          title = {Mruby integer overflow(CVE-2018-10191).},
          url = {https://github.com/mruby/mruby/issues/3995},
        }
        
        @misc{matiointegeroverflow,
          title = {Matio integer overflow(CVE-2020-19497).},
          url = {https://nvd.nist.gov/vuln/detail/CVE-2020-19497},
        }
        
        @misc{ezXMLdivide-by-zero,
          title = {Ezxml divide-by-zero(CVE-2021-30485).},
          url = {https://nvd.nist.gov/vuln/detail/CVE-2021-30485},
        }
        
        @misc{libpngdivide-by-zero,
          title = {Libpng divide-by-zero(CVE-2018-13785).},
          url = {https://nvd.nist.gov/vuln/detail/CVE-2018-13785},
        }
        
        @misc{libjpegdivide-by-zero,
          title = {Libjpeg divide-by-zero(CVE-2021-20205).},
          url = {https://nvd.nist.gov/vuln/detail/CVE-2021-20205},
        }
        
        @misc{libjpegheapbufferoverflow,
          title = {Libjpeg heap buffer overflow(CVE-2018-14495).},
          url = {https://nvd.nist.gov/vuln/detail/CVE-2018-14495},
        }
        
        @misc{libxml2nullptrdereference,
          title = {Libxml2 nullptr dereference(CVE-2017-7595).},
          url = {https://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2017-7595},
        }
        
        @misc{libsixelnullptrdereference,
          title = {Libsixel nullptr dereference(CVE-2021-45340).},
          url = {https://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2021-45340},
        }
        
